A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw
Addressing reviewer 3 comment
2) This part doesn't make sense:

"In general, a distributed volunteer-based evolutionary computation
system based on the browser is simply a client-server system which
client is embedded in the browser via JavaScript. We call this system
NodIO."

It's either a general statement, or it's a system called NodIO. It can't
be both. Please tidy up the wording.

In general, a distributed volunteer-based evolutionary computation
system based on the browser is simply a client-server system
which client is embedded in the browser via JavaScript. We call this
system {\sf NodIO}. All parts of the framework are free and available
with a free license from \url{https://ANONYMOUS-URL}.
%\url{https://github.com/JJ/splash-volunteer}.

>>>>

In this section we present {\sf NodIO}, a distributed volunteer-based 
evolutionary computation system immplemented in JavaScript. 
All parts of the framework are free and available
with a free license from \url{https://ANONYMOUS-URL}.
%\url{https://github.com/JJ/splash-volunteer}.
